Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-01-03 lqg-strings.tex
Fixed a typo in sec 4

In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov string. we start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
\begin{multline} \label{eqn:inverse-metric-Polyakov}
	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{multline}
The equations of motion for the world-sheet metric are completely unchanged by this correction, so they are
\begin{equation} \label{eqn:vary-wrt-g}
	\frac{\delta S_{I A P}}{\delta g^{c d}} \overset{!}{=} 0
\end{equation}
from which we obtain the stress-energy tensor for the worldsheet:
\begin{multline} \label{eqn:inverse-area-em-tensor}
	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0 ,
\end{multline}
from which we can extract the metric $g_{c d}$ as
\begin{equation} \label{eqn:ws-metric}
	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f$ is given by
\begin{equation} \label{eqn:inverse-area-f}
	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{equation}

@@

The \textquotedblleft Virasoro-Klein-Gordon" algebra our constraint modes satisfy is given by
\begin{equation} \label{eqn:L-commutators-1}
	\Big[ \Hat{L}_{n , m} , \Hat{L}_{p , k} \Big] = 0
\end{equation}
\begin{multline} \label{eqn:L-commutators-2}
	\Big[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{m - n}{E_{m - n}} \Big( \Hat{L}_{n + k - p , n} \delta _{n - m , k} + \\
	+ \Hat{L}_{n - m + k - p , n - m} \delta _{n , k} \Big)
\end{multline}
\begin{multline} \label{eqn:L-commutators-3}
	\Big[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{(m - n)}{E_{m - n}} \frac{(k - p)}{E_{k - p}} \times \\
	\times \Bigg( \frac{E_{- n}}{(- n)} \Hat{\widetilde{L}}_{k - p - n , k - p} \delta _{n - m , k} + \\
	+ \frac{E_{- k}}{(- k)} \Hat{\widetilde{L}}_{n - m - k , n - m} \delta _{n , k - p} \Bigg)
\end{multline}

>>>>

In the same way we considered the quantum geometry inverse metric correction to the Nambu-Goto action, it is also natural to consider such correction to the Polyakov string. We start with the action(\ref{eqn:polyakov-gravity}) and proceed with the inverse area correction(\ref{eqn:inverse-metric-correction}), which yields our corrected Polyakov action
\begin{multline} \label{eqn:inverse-metric-Polyakov}
	S_{I A P} = - \frac{T}{2} \int \diff ^2 x \left( \sqrt{- g} - \frac{k \Delta}{2 \sqrt{- g}} \right) \times \\ \times g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{multline}
The equations of motion for the world-sheet metric are completely unchanged by this correction, so they are
\begin{equation} \label{eqn:vary-wrt-g}
	\frac{\delta S_{I A P}}{\delta g^{c d}} \overset{!}{=} 0
\end{equation}
from which we obtain the stress-energy tensor for the worldsheet:
\begin{multline} \label{eqn:inverse-area-em-tensor}
	T_{c d} := \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} - \\ - \frac{1}{2} g_{c d} g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} = 0 ,
\end{multline}
from which we can extract the metric $g_{c d}$ as
\begin{equation} \label{eqn:ws-metric}
	g_{c d} = 2 f \partial _{c} X^{\mu} \partial _{d} X^{\nu} G_{\mu \nu} ,
\end{equation}
where the function $f$ is given by
\begin{equation} \label{eqn:inverse-area-f}
	\frac{1}{f} = g^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} G_{\mu \nu} .
\end{equation}

@@

The \textquotedblleft Virasoro-Klein-Gordon" algebra our constraint modes satisfy is given by
\begin{equation} \label{eqn:L-commutators-1}
	\Big[ \Hat{L}_{n , m} , \Hat{L}_{p , k} \Big] = 0
\end{equation}
\begin{multline} \label{eqn:L-commutators-2}
	\Big[ \Hat{L}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{m - n}{E_{m - n}} \Big( \Hat{L}_{n + k - p , n} \delta _{n - m , k} + \\
	+ \Hat{L}_{n - m + k - p , n - m} \delta _{n , k} \Big)
\end{multline}
\begin{multline} \label{eqn:L-commutators-3}
	\Big[ \Hat{\widetilde{L}}_{n , m} , \Hat{\widetilde{L}}_{p , k} \Big] = \frac{(m - n)}{E_{m - n}} \frac{(k - p)}{E_{k - p}} \times \\
	\times \Bigg( \frac{E_{- n}}{(- n)} \Hat{\widetilde{L}}_{k - p - n , k - p} \delta _{n - m , k} + \\
	+ \frac{E_{- k}}{(- k)} \Hat{\widetilde{L}}_{n - m - k , n - m} \delta _{n , k - p} \Bigg) .
\end{multline}
